Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-15 manuscript/manuscript.tex
Started writing conclusions

>>>>

\section{Conclusions}

We have developed a Python library that allows us to perform forward gravity computations using tesseroids with variable density in depth.
The code numerically approximates the integral that defines the gravity potential, its gradient and the Marussi tensor through the Gauss-Legendre Quadrature (GLQ).
It essentially consists in approximating the gravity fields of the tesseroids with the effect of point masses located on the scaled nodes of the Legendre polynomials.
We state that this method it's well suited to approximate the effect of tesseroids with arbitrary densities, in contrast with the ones that involves Taylor series expansion.

Although this new code uses only second order GLQ on each integration, we've enhanced its accuracy through a modified adaptive discretization method. It divides the tesseroid by half if the ratio of the distance to the computation point and its size is lower than a predefined distance-size ratio $D$.
We can summarise that $D$ controls the accuracy of the method: a higher value of $D$ generates more divisions of the tesseroids, thou more point masses, what leads to a more precise approximation.

On the other hand, there's no direct relation between the value of $D$ and the error of the computation, that's why we had to determine the minimum value of $D$ for each gravity magnitude that produces an acceptable accuracy.
These distance-size ratio determinations have been made through the comparison of the numerical approximation with the analytical solutions for the exceptional case of a spherical shell.
From the wide range of possible density variations, we've chosen a (1) linear, (2) an exponential and (3) a discontinuous density functions.

The tests over the first two functions have shown that in order to achieve an accuracy of 0.1\%, a value of $D$ equal to 1, 2 and 8 must be used in the calculation of the gravity potential, its gradient components and the components of the Marussi tensor, respectively.
We have also found a limitation on the variation of the exponential density function: the absolute value of the exponent must not be greater than 1.
However, those extremely variations cannot be found inside the Earth, so this limitation does not determines a true restriction for real life models.

On the other hand, the tests over the discontinuous function were not satisfactory.
In such cases we recommend to divide the model in several tesseroids, each one with a specific homogeneous density or a continuous density function, instead of using one variable density tesseroid.
